Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-02-20 paper/main.tex
Preparing for camera ready

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

@@

\subsubsection*{Acknowledgments}
Acknowledgements removed for anonymous submission.
%We would like to acknowledge Kevin Bowers, Alex Meiburg, JD Co-Reyes, Carson
%McNeil, Andy Palan, and several others for fruitful conversations and guidance.

>>>>

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

The parallel linear recurrence CUDA kernel and TensorFlow bindings are
available at \url{https://github.com/eamartin/parallelizing_linear_rnns} .

@@

\subsubsection*{Acknowledgments}
We would like to acknowledge Kevin Bowers, Alex Meiburg, JD Co-Reyes, Carson
McNeil, Andy Palan, and several others for fruitful conversations and guidance.
